Installation of libraries

```{r}
library(caret)
setwd("C:/Work/Coding/DataScienceCP")

```

Reading the csv

```{r}
nhanes_dataset <- read.csv("CardiacPrediction.csv")
nhanes_dataset$CoronaryHeartDisease = as.factor(nhanes_dataset$CoronaryHeartDisease)
set.seed(123)
```

Creating train and test datasets

```{r}
trainIndex <- createDataPartition(nhanes_dataset$CoronaryHeartDisease, p = 0.75, 
                                  list = FALSE, 
                                  times = 1)
train_data <- nhanes_dataset[trainIndex,]
test_data <- nhanes_dataset[-trainIndex,]

train_data

```

---
title: 10-Fold Cross Validation
---

```{r}
# 10-fold cross validation with 3 repeats
trainControl <- trainControl(method="repeatedcv", number=10, repeats=3, verboseIter = TRUE)

metric <- "Accuracy"
```

---
title: # Bagged CART
---

```{r}
set.seed(7)
fit.treebag <- train(CoronaryHeartDisease~., data = train_data, method = "treebag", metric = metric,trControl = trainControl)

```

---
title: Random Forest Algorithm
---

```{r}
# RF
set.seed(7)
fit.rf <- train(CoronaryHeartDisease~., data = train_data, method = "rf", metric = metric,trControl = trainControl)
```

---
title: GBM - Stochastic Gradient Boosting
---

```{r}
set.seed(7)
fit.gbm <- train(CoronaryHeartDisease~., data = train_data, method = "gbm",metric = metric,trControl = trainControl, verbose = FALSE)
```

---
  title: C5
---

```{r}
set.seed(7)
fit.c50 <- train(CoronaryHeartDisease~., data = train_data, method = "C5.0", metric = metric,trControl =trainControl)
```

---
  title: LG - Logistic Regression
---

```{r}
set.seed(7)
fit.glm <- train(CoronaryHeartDisease~., data = train_data, method="glm",
                 metric=metric,trControl=trainControl)
```

---
  title: LDA - Linear Discriminate Analysis 
---

```{r}
set.seed(7)
fit.lda <- train(CoronaryHeartDisease~., data = train_data, method="lda",
                 metric=metric,trControl=trainControl)
```

---
title: K-Nearest Neughbours
---

```{r}
set.seed(7)
fit.knn <- train(CoronaryHeartDisease~., data = train_data, method="knn",
                 metric=metric,trControl=trainControl)
```

---
title: Naive Bayes(NB)
---

```{r}
set.seed(7)
Grid = expand.grid(usekernel=TRUE,adjust=1,fL=c(0.2,0.5,0.8))
fit.nb <- train(CoronaryHeartDisease~., data = train_data, method="nb",
                 metric=metric,trControl=trainControl,
                tuneGrid=Grid)
```

---
title: Saving the trained models to files
---

```{r}
saveRDS(fit.rf, "trainedRF_model.rds")
saveRDS(fit.treebag, "trainedBCART_model.rds")
saveRDS(fit.gbm, "trainedgbm_model.rds")
saveRDS(fit.c50, "trainedc50_model.rds")
saveRDS(fit.glm, "trainedglm_model.rds")
saveRDS(fit.lda, "trainedlda_model.rds")
saveRDS(fit.knn, "trainedknn_model.rds")
saveRDS(fit.nb, "trainednb_model.rds")
```
